---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statDIST

<!-- badges: start -->
<!-- badges: end -->

The goal of statDIST is to make learning fundamental statistics concepts easier. At the core of this package is the `sample_generator()` function, which allows one to generate any number of samples containing any number of measurements up to one less than a hypothetical population distribution that is user-defined. 

The fundamental premise is that **seeing** data as it is transformed is much better than memorizing formulas. 

## Installation

You can install the development version of statDIST from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("CodetoDrum/statDIST")
```

## Example

Everything starts by generating samples to experiment with. The initial creation of this function was motivated by a desire to generate sampling distributions to actually *see* the concept in action.

```{r}
test_samples <- statDIST::sample_data(
  num_samples = 10,
  sample_size = 25,
  dist_size = 500,
  max_val = 250
)

head(test_samples)
```

